\documentclass[a4,10pt]{article}


\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
 \usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{hyperref}
\usepackage{csquotes}
\usepackage{tabularx}
\hypersetup{colorlinks=true,urlcolor=black}
\usepackage[11pt]{moresize}
\usepackage{setspace}
\usepackage{fontspec}
\usepackage{fontawesome5}
\usepackage[inline]{enumitem}
\usepackage{array}
\usepackage{xcolor}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
\usepackage{anyfontsize}

%%%% Set Margins
\usepackage[margin=1cm, top=1cm]{geometry}

%%%% Set Fonts
\setmainfont[
BoldFont=SourceSansPro-Semibold.otf, %SourceSansPro-Bold.otf
ItalicFont=SourceSansPro-RegularIt.otf
]{SourceSansPro-Regular.otf}
\setsansfont{SourceSansPro-Semibold.otf}

%%%% Set Page
\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

%%%% Set URL Style
\urlstyle{same}

%%%% Set Indentation
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%%%% Set Secondary Color
\definecolor{UI_blue}{RGB}{32, 64, 151}

%%%% Define New Commands
\usepackage[style=nature, maxbibnames=3]{biblatex}
\addbibresource{Publications.bib}

%%%% Bold Name in Publications
\renewcommand*{\mkbibnamegiven}[1]{%
\ifitemannotation{highlight}
{\textbf{#1}}
{#1}}

\renewcommand*{\mkbibnamefamily}[1]{%
\ifitemannotation{highlight}
{\textbf{#1}}
{#1}}

%%%% Set Sections formatting
\titleformat{\section}{
\color{UI_blue} \scshape \raggedright \large 
}{}{0em}{}[\vspace{-10pt} \hrulefill \vspace{-6pt}]

%%%% Set Subtext Formatting
\newcommand{\subtext}[1]{
#1\par\vspace{-0.2cm}}

% \newcommand{\subtextit}[1]{\vspace{0.15cm}
% \textit{ #1 \vspace{-0.2cm}} }

%%%% Set Item Spacing
\setlist[itemize]{align=parleft,left=0pt..1em}

%%%% New Itemize "Zitemize" Formatting - tighter spacing than itemize
\newenvironment{zitemize}{
\begin{itemize}\itemsep0pt \parskip0pt \parsep1pt}
{\end{itemize}\vspace{-0.5cm}}


%%%% Define Skills Bold Formatting
\newcommand{\hskills}[1]{
\textbf{\bfseries #1} }

%%%% Set Subsection formatting
\titleformat{\subsection}{\vspace{-0.1cm} 
\bfseries \fontsize{11pt}{2cm}}{}{0em}{}[\vspace{-0.1cm}]
\titlespacing*{\section}{0pt}{7pt plus 1pt minus 1pt}{5pt plus 1pt minus 1pt}
\titlespacing*{\subsection}{0pt}{5pt plus 1pt minus 1pt}{3pt plus 1pt minus 1pt}


\begin{document}

%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  HEADER
%%%%%%% --------------------------------------------------------------------------------------
\begin{center}
    \begin{minipage}[b]{0.24\textwidth}
            \large +919539846630 \\
            \large \href{mailto:mohameddanisap@gmail.com}{mohameddanisap@gmail.com} 
    \end{minipage}% 
    \begin{minipage}[b]{0.5\textwidth}
            \centering
            {\Huge MOHAMED DANIS. AP} \\ %
            \vspace{0.1cm}
            {\color{UI_blue} \Large{FULLSTACK ENGINEER}} \\
             \href{https://portfolio.mdanis.tech/}{\color{UI_blue} \textbf{view my portfolio}}
    \end{minipage}% 
    \begin{minipage}[b]{0.24\textwidth}
            \flushright \large  %Willing to Relocate
           {\faLinkedin\ \href{https://www.linkedin.com/in/mohamed-danis/}{LinkedIn}} \\
{\faGithub\ \href{https://github.com/MohamedDanis}{Github}}
    \end{minipage}   
        
\end{center}
\section{Profile Summary}
\begin{minipage}[b]{\textwidth}
\normalsize  % Ensure uniform font size
\textbf{Fullstack Engineer} with \textbf{2 years of experience} specializing in building \textbf{scalable web applications}. Proficient in modern stacks, including \textbf{React}, \textbf{Angular}, \textbf{TypeScript}, and \textbf{JavaScript}. Experienced in developing \textbf{reusable components}, optimizing UI for performance and accessibility, and integrating \textbf{API} services, with a strong foundation in both \textbf{Frontend} and \textbf{Backend} technologies adhering to full \textbf{SDLC} practices from design to deployment. Passionate about turning complex technical challenges into simple \textbf{user-centric solutions} while fostering \textbf{collaboration} and sharing best practices with the team.
\end{minipage}

\section{Experience}

\subsection*{FULLSTACK DEVELOPER \hfill Nov 2023 --- Present} \subtext{Tefora Software Solutions \hfill Malappuram, Kerala} \begin{itemize}[itemsep=2.2pt, parsep=1pt]
\item Engineered a scalable Progressive Web App (PWA) for a hospital indoor navigation using  \textbf{ReactJS}, and \textbf{TypeScript}, which reduced client costs by \textbf{70\%} and saved user time by \textbf{50\%} through robust offline capabilities.
    \item Led a 2-member development team to build multiple comprehensive \textbf{React} based \textbf{SEO} friendly school website \textbf{CMS}, successfully delivering the entire solution from concept to completion within a \textbf{30-day} timeframe.
    \item Managed \textbf{DevOps} and \textbf{CI/CD} initiatives, streamlining project deployment and leveraging expertise in \textbf{Next.js}, \textbf{Express.js}, and \textbf{TypeScript} to build scalable web applications.
    \item Part of the research and development team to build \textbf{AI Saas} application for meeting agents.
    \item Utilized \textbf{n8n}(Workflow Automation \& AI agents) internally to boost the processes with client onboarding, scrape email for lead generation and automated image generation etc.
    \item Stepped into a complex \textbf{LMS} project mid-development, rapidly assessing the codebase and project requirements to ensure smooth progress.
    \item Demonstrated high-efficiency project delivery by developing and deploying single-page \textbf{React} sites from concept to completion in an average of \textbf{10 hours}.
\end{itemize}

\section{Technical Skills}
\begin{itemize}[itemsep=0.5pt, parsep=0.5pt]  % Made bullet points consistent
    \item \textbf{Languages/Frameworks:} JavaScript (ES6+), TypeScript, Python, ReactJS, Next.js, Node.js, Express.js, Nest.js, Redis, Redux, Zustand, Vercel AI
    \item \textbf{Front-End:} TailwindCSS, Bootstrap, MUI, Shadcn/ui, HTML5, CSS3, Motion, GSAP, SEO, SSR, SSG, Responsive design, State Management
    \item \textbf{DevOps\&Tools:} Git, GitHub, GitHub Actions, Docker (basics), Docker Compose, MCP Containerization, DigitalOcean, AWS (EC2, S3, SQS, EventBridge, Lambda), Vite, Webpack (familiarity), Postman, Jira, Swagger, Vercel
    \item \textbf{Databases/ORM:} MongoDB, Postgresql, Mongoose, Drizzle ORM, Sequelize
    \item \textbf{APIs:} RESTful APIs, GraphQL APIs, Server Actions
    \item \textbf{Testing \& Practices:} Agile, Scrum, CI/CD, Vitest, Jest, Unit Testing
\end{itemize}

\section{Education }
\subsection*{B.Tech (CSE) {\normalsize \normalfont APJ Abdul Kalam Technological University, GPA: 7.3/10.00} \hfill Aug 2019 --- Jul 2023} 
\vspace{0.1cm}
\subsection*{Higher Secondary (Biology Science) {\normalsize \normalfont Kerala Board of Higher Secondary Education} \hfill 2017 Jun --- 2019 Mar} 
\vspace{0.1cm}

\section{Projects}
\vspace{2.5pt}
  % Reduced space before the first subsection
\subsection{InterviewGenie $|$ \small{\href{https://interview-mvp-sooty.vercel.app/}{Live Link}}}
\begin{itemize}[itemsep=1pt, parsep=1pt]  % Keep item spacing compact
    \item Developed this project as part Top100 coders hackathon in 2023, it's an AI Agent to practice mock interviews spanning from \textbf{200+ domains} using Gemini API LLM.
    \item Deliver interview insights and feedbacks within \textbf{5 seconds} timeframe.
    \item \textbf{70\%} of software developers who tested had great result.
    \item Utilized Next.JS, Vercel AI SDK, Better-Auth, Drizzle ORM, Clean UI using TailwindCSS and Shadcn/UI.
\end{itemize}

\vspace{-8pt}  % Reduced space between subsections
\subsection{Opnhub $|$ \small{\href{https://opnhub.vercel.app/}{Live Link}}}
\begin{itemize}[itemsep=1pt, parsep=1pt]  % Keep item spacing compact
    \item Build this personal project to help software developers to find opensource projects.
    \item Utilized \textbf{NextJS}, RESTFul APIs from github to create a dead simple tool.
    \item Published in producthunt and gained \textbf{20+ upvotes}.
    \item Released as opensource project and received contributions from \textbf{10+} developers from around the world.
\end{itemize}

\section{Achievements}
\vspace{-0.5pt}  % Reduced space before the first subsection
\begin{itemize}[itemsep=1pt, parsep=1pt]  % Keep item spacing compact
  \item Became finalist at \textbf{Top100 Coders} in Huddle Global 2023.
\end{itemize}


%%%%%%% ---------------------------- END DOC HERE ---------------------------- %%%%%%% 
\end{document}